### 2021-04-16 0_coverletter/itt-emotion-coverletter.tex
7-2 cover letter improved. READY FOR SUBMISSION

\addtolength{\headheight}{-11em}
\addtolength{\textheight}{10em}
\addtolength{\textwidth}{8em}
\addtolength{\oddsidemargin}{-6em}

@@

We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem. Therefore, in this revision, we made a few changes to the structure of section "3. Theoretical background and hypothesis development", adding more literature we reviewed, and added to the Abstract, Introduction, and Research objective sections as well.

>>>>

\addtolength{\headheight}{-11em}
\addtolength{\textheight}{20em}
\addtolength{\textwidth}{10em}
\addtolength{\oddsidemargin}{-6em}

@@

We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem to heart. In our revision, we explain further our theoretical interest in the differences between Chinese and Western tourists when faced with Japanese hospitality, and other factors in Japanese hotels. A cross-cultural examination of the satisfaction for these factors is indeed our main purpose.

In our literature review, we explain how satisfaction is the realization of an expectation, or rather, the perception of that realization. The difference between expectation and perception is what amounts to satisfaction. However, we find that both expectations and perceptions of quality are heavily influenced by cultural backgrounds. So not only is the expectations tourists would have when visiting Japan, but after experiencing the services influenced by the \textit{Omotenashi} culture, their perceptions of these services can be different. Adding to that, the numbers of tourists in Japan is increasing, and Chinese and Western tourists are the two largest populations of tourists. This is the reasoning behind our interest in this research problem.

Therefore, in this revision, we made a few changes to the structure of section "3. Theoretical background and hypothesis development", adding more literature we reviewed to back our interest in this research, and added to the Abstract, Introduction, and Research objective sections as well.
